Digital Analysis of Paintings

### 2014-04-26 paper.tex
Write up paper 7.

\newacronym{RGB}{RGB}{Red, Green, Blue}

@@

>>>>

\newacronym{APICSS}{APICSS}{Art Painting Image Color Semantics}
\newacronym{RGB}{RGB}{Red, Green, Blue}
\newacronym{HSL}{HSL}{Hue, Saturation, Luminance}
\newacronym{HSV}{HSV}{Hue, Saturation, Value}

@@

The distribution of colour across an image can give a surprising amount of
information about that image, especially given that colour is very subjective
to an individual.

Ivonna, Stanchev and Dimitrov investigated the colour
distribution within the works of over 100 artists for several different
countries and periods, using a system named \gls{APICSS}\cite{ivanova2008analysis}.

Existing systems already statistically analysed colours within an image and
some even used classifiers, typically a naive Bayesian classifier as it fits
well with statical methods, to perform extra analysis.

Unlike these existing system, \gls{APICSS} focused primarily on the \gls{HSL}
colour space as it is the closest representation to an artist's colour wheel.
\gls{HSV} was also considered, but because the lightness is not symmetrical
within the \gls{HSV} colour space, it is less useful for direct comparison.

As with any system involving classification, a feature space is needed to
represent an item within the data set. In the case of \gls{APICSS} the feature
space is three dimensional, one for each of the values in the colour space.

From this, a distance measure (in this case Euclidean distance) can be used to
compare different items.

\gls{APICSS} also take into account some of the metadata attached to each
painting, such as the movement and sub-movement during which the painting was
created. This allows for more statistical analyses to be performed on sub-sets
of the data set.

\gls{APICSS} appears to be a good system, which considers both metadata and
analysis gained from the digitisation of artwork. The paper considers a wide
range of artists and periods.

However, the use of a lossy image format (JPEG) could potentially skew the
results. The system itself is very basic, especially if it only considers
\gls{HSL} and metadata. This is further compounded by only considering thirteen
colours within the Hue (twelve separate colours and one achromatic).

Despite having a decent sized data set overall, some of the categories have
relatively small items within them.

Overall \gls{APICSS} is a good application of existing research, but uses very
basic analysis techniques on the images themselves.
